data wrangling and plots

### 2021-02-22 shared analysis files /data_wrangling_plot22feb.Rmd
additional changes, adjusting size of points

```{r, echo= FALSE}
# scatterplot of standardized mean response vs mean temp faceted by org level and colored by flux_range
ggplot(dat_MA_ES, aes(x=mean_temp_constant, y=yi, color = as.factor(flux_range)))+
  geom_point()+
  facet_wrap(~org_level)+
  theme_bw()+
  ggtitle("SMD across mean temperature colored by fluctation range 
          and faceted by organization level")
```

@@

```{r, echo= FALSE}
ggplot(normalized, aes(y=yi, x=flux_range, color = genus))+
  geom_jitter(alpha = 0.5)+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by genus")
```

@@

```{r, echo= FALSE}
ggplot(common_unit_C, aes(y=yi, x=study_id, color = as.factor(flux_range)))+
  geom_point(alpha = 0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the common unit C (CT assays)")
```

```{r, echo= FALSE}
#plot across studies with common unit gram
ggplot(common_unit_g, aes(y=yi, x=flux_range, color = study_id))+
  geom_point(alpha =0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle("SMD across fluctuation ranges colored by studies with the common unit grams")
```

>>>>

```{r, echo= FALSE}
# scatterplot of standardized mean response vs mean temp faceted by org level and colored by flux_range
ggplot(dat_MA_ES, aes(x=mean_temp_constant, y=yi, color = as.factor(flux_range)))+
  geom_point(alpha=0.5, size =3)+
  facet_wrap(~org_level)+
  theme_bw()+
  ggtitle("SMD across mean temperature colored by fluctation range 
          and faceted by organization level")
```

@@

```{r, echo= FALSE}
ggplot(normalized, aes(y=yi, x=flux_range, color = genus))+
  geom_jitter(alpha = 0.5, size =3)+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by genus")
```

@@

```{r, echo= FALSE}
ggplot(common_unit_C, aes(y=yi, x=study_id, color = as.factor(flux_range)))+
  geom_point(alpha = 0.5, size=7)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the common unit C (CT assays)")
```

```{r, echo= FALSE}
#plot across studies with common unit gram
ggplot(common_unit_g, aes(y=yi, x=flux_range, color = study_id))+
  geom_point(alpha =0.5, size =6)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle("SMD across fluctuation ranges colored by studies with the common unit grams")
```
